Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-04 overall.tex
minor fixes Section IV.

Currently, ATLAS deploys 20 instances of the PanDA Broker on 4 Titan's DTNs,
5 instances per DTN\@. Each broker submits and manages the execution of 15 to
300 ATLAS jobs, one job for each Titan's worker node, and a theoretical
maximum concurrent use of 96,000 cores. Since November 2015, PanDA Brokers
have operated only in backfill mode, without a defined time allocation, and
running at the lowest priority on Titan. Therefore, ATLAS contributed to
increase the Titan's overall utilization without affecting other users.

>>>>

Currently 20 instances of the PanDA Broker are deployed on 4 Titan's DTNs,
with 5 instances per each DTN\@. Each broker submits and manages the execution
of 15 to 300 ATLAS jobs, one job for each Titan's worker node, and a
theoretical maximum concurrent use of 96,000 cores. Since November 2015, PanDA
Brokers have operated only in backfill mode, without a defined time
allocation, and running at the lowest priority on Titan. Therefore, ATLAS
contributed to an increase of Titan's overall utilization without affecting
other users.
